Decentralized Data Marketplace to Enable Trusted Machine Economy

### 2019-08-29 paper.tex
Fix denotation

\begin{document}
%
\title{Decentralized Data Marketplace to Enable Trusted Machine Economy}
%
\author{
%%% Fill in name here
\IEEEauthorblockN{Zan-Jun Wang\IEEEauthorrefmark{3}, Ching-Hua Lin\IEEEauthorrefmark{2}, Ching-Chun (Jim) Huang\IEEEauthorrefmark{1}}\\

@@

@@

>>>>

\begin{document}
%
\title{Decentralized Data Marketplace to Enable Trusted Machine Economy}
%
\author{
%%% Fill in name here
\IEEEauthorblockN{Zan-Jun Wang\IEEEauthorrefmark{3}, Ching-Hua Lin\IEEEauthorrefmark{2}, Yang-Hao Yuan\IEEEauthorrefmark{4}, Ching-Chun (Jim) Huang\IEEEauthorrefmark{1}}\\

@@

In our game theory model there are two kinds of players. One is data provider, and the other one is data buyer. Data provider would receive subscription fee for buying data each time the data is transmitted to data buyer.
The data buyer will keep buying data from data povider, only when the data sold by the data provider with high enough correct rate, $P_r$. We deonte this correct rate threshold with $\xi$.
Once the correct rate is lower than $\xi$, the data buyers would consider this data provider as a malicious data provider, and reject to buy the data from this data provider.

@@

\subsection{Game Theory Evaluation}

\subsubsection{Model Description}
Repeated game consists of serveral repetitions of some stage games. In each stage game, the action player takes will effect the actions that players are going to take in the future stages. Repeated game can be illustrated with a decision tree and described their payoff with discounted sum of payoff. Discounted sum of payoff can capture the idea that what the players truly pursue is the sum of payoff in all stages and payoff in different stages may varify.

We use a repeated game to express the scenario of our Data Marketplace. Figure.\ref{fig:decision_tree} shows the decision tree to depict the the repeated game we used. Each level in this decision tree represents each round of data transmission from data provider to data buyers, and the data buyers would pay subscription fee, $P_s$, in total to buy the data.

\begin{figure} \centering \includegraphics[width=3.3in]{img/decision_tree.png} \caption{Decision Tree}
    \label{fig:decision_tree} \end{figure}
For every $n$ round, the data provider would cost $C_{maintain}$ to maintain or enhance the sensors that data provider owns. We call this as a maintain period. Moreover, the value of data and the cost of maintenance will decrease as time pass, so we introduce a discount factor $\beta$ to depict this phenomena.

We have these following assumptions:
\begin{itemize}
\item  There is no any other data providers provide the same product in Data Marketplace. Therefore, we can consider each provider's behavior independently. That means this decision tree represent the behavior of only one data provider.
\item  More than 51\% of data buyers are among complete information exchange state. In other words, once one of them launches voting for stopping buying data and refunding, they would succeed in refund voting.
\item  One of the data buyers who has complete imformation exchange with other 51\% buyers will definitely find out the wrong or fake data provided by data provider is wrong.
\end{itemize}

Based on the description above, the discount sum of payoff for our repeated game is 
\begin{equation} \label{payoff}
\sum_{i=0}^{m}{\beta^{in}\cdot [(\sum_{j=0}^{n} \beta^j \cdot P_s) - C_{maintain}]}
\end{equation}

\begin{itemize}
\item $P_s$ is the sum of subscription price (fee) for all subscriber.
\item $C_{maintain}$ is the cost of sensor maintenance in $n$ round.
\item $\beta$ is discounted factor.
\item $n$ is how many round for one maintenance period.
\item $m$ is how many maintenance periods have been experienced in this repeated game.
\end{itemize}

Al-Fagih et al. presented\cite{DataPrice} $P_s$ is a sigmoid function of $P_r$, and based on rule of thumb $C_{maintain}$ is about a exponential function of $P_r$. We can substitute $P_s$ and $C_{maintain}$ with $P_r$ into Eq. (\ref{payoff}), then we can find out the Nash Equilibrium of repeated game with differential easily.
